Covariate Analysis of MAYO Reprocessed counts Regressing out Diagnosis as well for TWAS

### 2020-05-23 code/prepscripts/MSBB_TranscriptNorm.Rmd
Trans DE MSBB
File Paths Fix

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
#BiocManager::install("biomaRt")
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)
#cl = makeCluster(detectCores()-2)
cl = makeCluster(14)
registerDoParallel(cl)
options(xtable.type="html")
setwd('~/AD_TargetRank/code/')
# Source modified utility functions from limma and sva package
source('../utilityFunctions/parallelDuplicateCorrelation.R')
source('../utilityFunctions/irwsva.build.R')
source('../utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

@@

#_#stopCluster(cl)
```

```{r DelFiles, echo=T, results='hide'}
#system('rm *.tsv')
```
### R Source Code
[Github](`r thisFile`)

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
#BiocManager::install("biomaRt")
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)
#cl = makeCluster(detectCores()-2)
cl = makeCluster(14)
registerDoParallel(cl)
options(xtable.type="html")
setwd('~/AD_TargetRank/code/')
# Source modified utility functions from limma and sva package
source('~/AD_TargetRank/utilityFunctions/parallelDuplicateCorrelation.R')
source('~/AD_TargetRank/utilityFunctions/irwsva.build.R')
source('~/AD_TargetRank/utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

@@

stopCluster(cl)
```

```{r DelFiles, echo=T, results='hide'}
system('rm *.tsv')
```
### R Source Code
[Github](`r thisFile`)

### 2020-05-23 code/prepscripts/Mayo_TranscriptNorm.Rmd
File Paths Fix

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
#BiocManager::install("biomaRt")
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)
#cl = makeCluster(detectCores()-2)
cl = makeCluster(14)
registerDoParallel(cl)
options(xtable.type="html")
setwd('~/AD_TargetRank/code/')
# Source modified utility functions from limma and sva package
source('../../utilityFunctions/parallelDuplicateCorrelation.R')
source('../../utilityFunctions/irwsva.build.R')
source('../../utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
#BiocManager::install("biomaRt")
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)
#cl = makeCluster(detectCores()-2)
cl = makeCluster(14)
registerDoParallel(cl)
options(xtable.type="html")
setwd('~/AD_TargetRank/code/')
# Source modified utility functions from limma and sva package
source('~/AD_TargetRank/utilityFunctions/parallelDuplicateCorrelation.R')
source('~/AD_TargetRank/utilityFunctions/irwsva.build.R')
source('~/AD_TargetRank/utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```
